Computer Science House Constitution

### 2024-04-08 constitution.tex
Fix subsection-related organization errors (#219)
Co-authored-by: Sam Cordry <samcodry@gmail.com>

\asubsection{Selection of the Operational Communications Director}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters

@@

\asubsection{Selection of Ad Hoc Directors}
\begin{enumerate}
	\item When a group of members feels an Ad Hoc Directorship is necessary, they present their plans to E-Board.
	      An E-Board Vote is taken to determine whether directorship status is granted.
	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budget, and membership considerations are defined.
\end{enumerate}

\asubsection{Selection of the Secretary}
E-Board may select any interested Active Member as Secretary.
The selection process can be an informal appointment, or follow an election process similar to other voting E-Board positions.

\asection{Executive Board Resignations}
An E-Board Member may resign from their E-Board position by submitting in writing the reason for resignation to the Chair.
The E-Board resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new director, as described in section \ref{Appointment of an Interim Director}, will begin at that time.
Following a resignation, the selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.

\asection{Appointment of an Interim Director}
The duties and responsibilities of a vacated office are assumed by an Active Member that is appointed at the Chair's discretion until the new director takes office. % It is often the Chair that assumes the responsibilities of that position
The vote of a vacated E-Board position shall be cast as an abstention in all E-Board matters where this vote is required to be cast.

\asubsection{Impeachment}
\begin{enumerate}
	\item Impeachment of any E-Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current members equaling or exceeding one-third the number of Eligible Votes, as defined in \ref{Eligible Votes}.
	\item The impeachment petition is then presented at an E-Board Meeting.
	      The member(s) initiating the petition present their case to E-Board.
	      E-Board then questions the accused member of the allegations.
	\item An E-Board Vote is taken on the impeachment petition, with all Voting E-Board Members present except the accused member who must be absent and whose vote counts as an Abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
	      If the majority of E-Board votes are negative, the petition and impeachment proceedings are dismissed.
	      This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current members equaling or exceeding two-thirds the number of Eligible Votes.
	\item If the majority of the E-Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a Secret Ballot Vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
	      Votes shall be collected and counted for a Two-Thirds Balloted Vote, as described in \ref{Balloted Vote}.
	\item A two-thirds quorum is necessary for the vote to be official.
	      If the resolution passes, the accused officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
	      If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	      A new selection and interim duty fulfillment procedure is followed similar to that of a resignation, as described in \ref{Executive Board Resignations}.
	\item The Secretary can be impeached according to the above process, or may be dismissed by an E-Board Vote.
\end{enumerate}

\asubsection{Term}
\begin{enumerate}
	\item The election process for the following year's E-Board members shall begin in the middle of spring semester.
	\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
	\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
	\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
	\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	      When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}

\asection{Appeals}
To initiate an appeal, a member must have the support of three Voting E-Board Members, or a petition with the signatures of one-third of Active Members.
After the appeal is presented, an E-Board Vote is taken to determine whether or not to overturn and reevaluate the decision.
If the vote passes, E-Board may discuss and make a new ruling by another E-Board Vote.

>>>>

\asubsubsection{Selection of the Operational Communications Director}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters

@@

\asubsubsection{Selection of Ad Hoc Directors}
\begin{enumerate}
	\item When a group of members feels an Ad Hoc Directorship is necessary, they present their plans to E-Board.
	      An E-Board Vote is taken to determine whether directorship status is granted.
	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budget, and membership considerations are defined.
\end{enumerate}

\asubsubsection{Selection of the Secretary}
E-Board may select any interested Active Member as Secretary.
The selection process can be an informal appointment, or follow an election process similar to other voting E-Board positions.

\asubsection{Executive Board Resignations}
An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
The E-Board resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new director, as described in section \ref{Appointment of an Interim Director}, will begin at that time.
Following a resignation, the selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.

\asubsection{Selection of an Acting Chairperson}
If there is not an acting Chair during a process where one is required, then the following line of succession is used to determine which director becomes the acting Chair until a new Chair is elected.
\begin{enumerate}
	\item[1.] Evals Director
	\item[2.] Financials Director
	\item[3.] Voting E-Board Member chosen by an E-Board Vote
\end{enumerate}

\asubsection{Appointment of an Interim Director}
The duties and responsibilities of a vacated office are assumed by an Active Member that is appointed at the Chair's discretion until the new director takes office. % It is often the Chair that assumes the responsibilities of that position
The vote of a vacated E-Board position shall be cast as an abstention in all E-Board matters where this vote is required to be cast.

\asubsubsection{Impeachment}
\begin{enumerate}
	\item Impeachment of any E-Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current members equaling or exceeding one-third the number of Eligible Votes, as defined in \ref{Eligible Votes}.
	\item The impeachment petition is then presented at an E-Board Meeting.
	      The member(s) initiating the petition present their case to E-Board.
	      E-Board then questions the accused member of the allegations.
	\item An E-Board Vote is taken on the impeachment petition, with all Voting E-Board Members present except the accused member who must be absent and whose vote counts as an Abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
	      If the majority of E-Board votes are negative, the petition and impeachment proceedings are dismissed.
	      This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current members equaling or exceeding two-thirds the number of Eligible Votes.
	\item If the majority of the E-Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a Secret Ballot Vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
	      Votes shall be collected and counted for a Two-Thirds Balloted Vote, as described in \ref{Balloted Vote}.
	\item A two-thirds quorum is necessary for the vote to be official.
	      If the resolution passes, the accused officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
	      If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	      A new selection and interim duty fulfillment procedure is followed similar to that of a resignation, as described in \ref{Executive Board Resignations}.
	\item The Secretary can be impeached according to the above process, or may be dismissed by an E-Board Vote.
\end{enumerate}

\asubsubsection{Term}
\begin{enumerate}
	\item The election process for the following year's E-Board members shall begin in the middle of spring semester.
	\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
	\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
	\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
	\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	      When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}

\asubsection{Appeals}
To initiate an appeal, a member must have the support of three Voting E-Board Members, or a petition with the signatures of one-third of Active Members.
After the appeal is presented, an E-Board Vote is taken to determine whether or not to overturn and reevaluate the decision.
If the vote passes, E-Board may discuss and make a new ruling by another E-Board Vote.
